Reproducible Summary Tables with gtsummary

### 2020-12-09 RJtemplate_gtsummary_submission.tex

% code for basic tbl_summary()
\begin{example}
tbl_summary_1 <-
  trial %>%
  select(age, grade, response, trt) %>%
  tbl_summary(by = trt)
\end{example}

>>>>

% code for basic tbl_summary()
\begin{example}
trial %>%
  select(age, grade, response, trt) %>%
  tbl_summary(by = trt)
\end{example}
\begin{figure}[h!]
  \includegraphics[height=5cm]{summary_basic.png}
  \centering
\end{figure}

% code for tbl_summary() with arguments
\input{tbl_tbl_summary_args.tex}
\begin{example}
trial %>%
  select(age, grade, response, trt) %>%
  tbl_summary(
    by = trt,
    type = all_continuous() ~ "continuous2",
    label = age ~ "Patient Age",
    statistic = list(all_continuous() ~ c("{N_nonmiss}", 
                                          "{mean} ({sd})", 
                                          "{median} ({p25}, {p75})", 
                                          "{min}, {max}"),
                     all_categorical() ~ "{n} / {N} ({p}%)"),
    digits = all_categorical() ~ c(0, 0, 1),
    missing = "no"
  )
\end{example}
\begin{figure}[h!]
  \includegraphics[height=5cm]{summary_plus.png}
  \centering
\end{figure}

% code for tbl_summary() with arguments
\input{tbl_tbl_summary_family.tex}
\begin{example}
trial %>%
  select(age, grade, response, trt) %>%
  tbl_summary(by = trt, missing = "no") %>%
  add_p(test = all_continuous() ~ "t.test",
        pvalue_fun = ~style_pvalue(., digits = 2)) %>%
  add_n()
\end{example}
\begin{figure}[h!]
  \includegraphics[height=5cm]{summary_plus_plus.png}
  \centering
\end{figure}
